---
title: "New Dataset"
author: "Hanxiao Lu"
date: "11/30/2018"
output: html_document
---
#WHAT ARE LEFT TO DO: BINNING some variables; generate trees; turn predict responses into 1 or 0 

```{r, results='hide'}
library(tidyr)
library(dplyr)
library(mosaic)
library(tree)
library(ISLR)
library(ggplot2)
library(class)
library(foreign)
library(readr)
```

##Names (eating disorder)
```{r, results='hide'}

#raw_data <- read.spss("...", to.data.frame = TRUE)
eatdisord_1 <- read_csv("Variblenamefiles/eatdisord_1.csv")
sub_use_1 <- read_csv("Variblenamefiles/sub_use_1.csv")
socnet<- read_csv("Variblenamefiles/socialnetworks.csv")
tobacco_1<- read_csv("Variblenamefiles/Tobacco_1.csv")
alcohol<- read_csv("Variblenamefiles/alcohol.csv")
social_ph<- read_csv("Variblenamefiles/Soicalph_1.csv")
persona<- read_csv("Variblenamefiles/personality_1.csv")
marriage<- read_csv("Variblenamefiles/marriage.csv")
ner_at<- read_csv("Variblenamefiles/nervous_attack.csv")
discrim<- read_csv("Variblenamefiles/discrimination.csv")
demograph<- read_csv("Variblenamefiles/demographics.csv")
family<- read_csv("Variblenamefiles/family.csv")
family_n_friends<- read_csv("Variblenamefiles/family_n_friends.csv")
depress<- read_csv("Variblenamefiles/depression.csv")
suicide<- read_csv("Variblenamefiles/Suicide.csv")

"Uncomment when uploading raw data however the raw dataset is too large for Git"
```

```{r, results='hide'}
#Read in Var names

#Main
eatdisord_1<- select(eatdisord_1, CPES, Eating_Disorder)
eatdisord_1= drop_na(eatdisord_1)

#CPES
CPES_ed= select(eatdisord_1, CPES)

#Full_explaination
full_name= select(eatdisord_1, Eating_Disorder)

#Make it a list
namelist = as.list(full_name)
'print(namelist)'
' We did not need this and can join on just the CPES code and maintain the information of the varible'
```

##Making Subset(eating disorder)

```{r, results='hide'}
data_ed= select(raw_data, CPES_ed$CPES[1:64])
```

#Substance varibles 
```{r, results='hide'}
#Main
sub_use_1<- select(sub_use_1, CPES)
sub_use_1= drop_na(sub_use_1)

#Make it a list
namelist_su = as.list(sub_use_1)
data_su= select(raw_data, sub_use_1$CPES[1:70])
```

#Tobacco
```{r, results='hide'}
#Main
tobacco_1<- select(tobacco_1, CPES)
tobacco_1= drop_na(tobacco_1)
#Make it a list
namelist_to = as.list(tobacco_1)
data_to= select(raw_data, tobacco_1$CPES[1:65])
```

#Social Phobia
```{r, results='hide'}
#Main
social_ph<- select(social_ph, CPES)
social_ph= drop_na(social_ph)
#Make it a list
namelist_sph = as.list(social_ph)
data_sph= select(raw_data, social_ph$CPES[1:87])
```

#Personality
```{r, results='hide'}
#Main
persona<- select(persona, CPES)
persona= drop_na(persona)
#Make it a list
namelist_per = as.list(persona)
data_per= select(raw_data, namelist_per$CPES[1:44])
```

#Marriage
```{r, results='hide'}
#Main
marriage<- select(marriage, CPES)
marriage= drop_na(marriage)
#Make it a list
namelist_mar = as.list(marriage)
data_mar= select(raw_data, namelist_mar$CPES[1:29])
```

#Social Networks

```{r, results='hide'}
#Main
socnet<- select(socnet, CPES)
socnet= drop_na(socnet)
#Make it a list
namelist_sn = as.list(socnet)
data_sn= select(raw_data, namelist_sn$CPES[1:15])
```

#Nervous Attack
```{r, results='hide'}
#Main
ner_at<- select(ner_at, CPES)
ner_at= drop_na(ner_at)
#Make it a list
namelist_nerv = as.list(ner_at)
data_nerv= select(raw_data, namelist_nerv$CPES[1:23])
```

#Discrimination

```{r, results='hide'}
#Main
discrim<- select(discrim, CPES)
discrim= drop_na(discrim)
#Make it a list
namelist_disc = as.list(discrim)
data_disc= select(raw_data, namelist_disc$CPES[1:13])
```

#Demographics
```{r, results='hide'}
#Main
demograph<- select(demograph, CPES)
demograph= drop_na(demograph)
#Make it a list
namelist_dem= as.list(demograph)
data_dem= select(raw_data, namelist_dem$CPES[1:14])
```

#Family Cohesion

```{r, results='hide'}
#Main
family<- select(family, CPES)
family= drop_na(family)
#Make it a list
namelist_fam = as.list(family)
data_fam= select(raw_data, namelist_fam$CPES[1:15])
```

#Family and Friends

```{r, results='hide'}
#Main
family_n_friends<- select(family_n_friends, CPES)
family_n_friends= drop_na(family_n_friends)
#Make it a list
namelist_ff = as.list(family_n_friends)
data_ff= select(raw_data, namelist_ff$CPES[1:39])
```

#Depression Espoide

```{r, results='hide'}
#Main
depress<- select(depress, CPES)
depress= drop_na(depress)
#Make it a list
namelist_dep = as.list(depress)
data_dep= select(raw_data, namelist_dep$CPES[1:5])
```

#Alcohol
```{r, results='hide'}
#Main
alcohol<- select(alcohol, CPES)
alcohol= drop_na(alcohol)
#Make it a list
namelist_alco = as.list(alcohol)
data_alco= select(raw_data, namelist_alco$CPES[1:5])
```


#Suicide
```{r, results='hide'}
#Main
suicide<- select(suicide, CPES)
suicide= drop_na(suicide)
#Make it a list
namelist_sui = as.list(suicide)
data_sui= select(raw_data, namelist_sui$CPES[1:12])
```

#combine all datasets into one 
```{r}
newdata <- cbind(data_alco, data_dem, data_dep, data_disc, data_ed, data_fam, data_ff, data_mar, data_nerv, data_per, data_sn, data_sph, data_su, data_sui, data_to)
```

#calculate the missing values from each variable (there are 500 of them!) and drop the ones with more than ... percent of missing values. play with it and apply methods for new results! 
```{r}
dat.5percent <- newdata[, -which(colMeans(is.na(newdata)) > 0.05)]
dat.10percent <- newdata[, -which(colMeans(is.na(newdata)) > 0.10)]
dat.20percent <- newdata[, -which(colMeans(is.na(newdata)) > 0.20)]
dat.25 <- newdata[, -which(colMeans(is.na(newdata)) > 0.25)]
```

```{r}
dat.25$V07655 <- as.numeric(dat.25$V07655)
dat.25$V07655[dat.25$V07655 == "2"] <- 0 
```

```{r}
dat.25 <- dat.25 %>%
  filter(dat.25$V01993 == "YES")
```

#boosting 
```{r}
library(gbm)
dat.25 <- dat.25 %>%
  filter(complete.cases(.))

set.seed(7)
train = dat.25%>%
  sample_frac(.5)
test = dat.25%>%
  setdiff(train)

boost.tree <- gbm(V07655~.-V07657 - V07876, data = train, distribution = "bernoulli", n.trees = 5000)

summary(boost.tree)


```


```{r}
par(mfrow = c(1,2))
plot(boost.tree, i = "V09414")
plot(boost.tree, i = "V09389")
```

```{r}
boost_estimate = predict(boost.tree,
newdata = test,
n.trees= 5000,
type="response")


```

```{r}
histogram(boost_estimate)
```

#check how many people have suicidal thoughts have endorsed depression
```{r}
dat.25 %>%
  filter(dat.25$V07655 == "1") %>%
  count()
```

#tree 

```{r}
tree1 <- tree(V07655~.-V07657-V07876, data = train)
summary(tree1)
plot(tree1)
text(tree1, pretty = 0)
```


#bagging and random forest 
```{r}
library(randomForest)
set.seed(1)
bag_boston = randomForest(medv~.,
data = boston_train,
mtry = 13,
importance = TRUE)
bag_boston
```

```{r}
tree_pred = predict(tree1, test, type = "class")
table(tree_pred, test$V07655)
```




```{r}
#excluding the variable if someone lives in the country or not 
tree2<- tree(V07657 ~.-V07655-V07876-V05700, data = train)
summary(tree)
plot(tree2)
text(tree2, pretty = 0)
```

```{r}
tree2
```

```{r}
tree_pred = predict(tree, test, type = "class")
table(tree_pred, test$V07657)
#number of correct predictions is about 78%. 

```

```{r}
tree_pred = predict(tree2, test, type = "class")
table(tree_pred, test$V07657)
#prediction correct rate 
```

#Tree Decision for predicting depression with 12month episode 
```{r}
set.seed(1)
train = dat.30percent%>%
  sample_n(10000)
test = dat.30percent%>%
  setdiff(train)

tree3<- tree(V07655~.-V07657-V07876, data = train)
plot(tree3)
text(tree3, pretty = 0)
```

```{r}
tree_pred = predict(tree3, test, type = "class")
table(tree_pred, test$V07655)
```

#Tree Decision for predicting depression with lifetime episode 
```{r}
set.seed(1)
train = dat.30percent%>%
  sample_n(10000)
test = dat.30percent%>%
  setdiff(train)

tree4<- tree(V07876~.-V07657-V07655, data = train)
plot(tree4)
text(tree4, pretty = 0)
```

```{r}
tree_pred = predict(tree4, test, type = "class")
table(tree_pred, test$V07876)
```

#with 10 percent missing values 
```{r}
dat.10percent[is.na(dat.10percent)] <- 5 
#assume all missing values are not endorsed cases
dat.10percent$V07655 = as.factor(dat.10percent$V07655)
dat.10percent$V07876 = as.factor(dat.10percent$V07876)

set.seed(3)
train = dat.10percent%>%
  sample_n(10000)
test = dat.10percent%>%
  setdiff(train)

tree5<- tree(V07655~.-V07876, data = train)
summary(tree5)
plot(tree5)
text(tree5, pretty = 0)
```







