---
title: "Main code"
author: "Margaret Perry"
date: "November 16, 2018"
output: pdf_document
---

```{r, echo=FALSE}
library(haven)
library(tidyr)
library(dplyr)
library(mosaic)
library(tree)
library(ISLR)
library(ggplot2)

```

##Names (eating disorder)
```{r}
library(readr)
library(haven)
<<<<<<< HEAD
raw_data <- read_sav("C:/Users/rocio/Downloads/20240-0001-Data.sav")
=======
raw_data <- read_sav("~/20240-0001-Data.sav")
>>>>>>> 9f42ce87ef64fa276feec6dc649c9561a2bbaefc
eatdisord_1 <- read_csv("Variblenamefiles/eatdisord_1.csv")
sub_use_1 <- read_csv("Variblenamefiles/sub_use_1.csv")
socnet<- read_csv("Variblenamefiles/socialnetworks.csv")
tobacco_1<- read_csv("Variblenamefiles/Tobacco_1.csv")
alcohol<- read_csv("Variblenamefiles/alcohol.csv")
social_ph<- read_csv("Variblenamefiles/Soicalph_1.csv")
persona<- read_csv("Variblenamefiles/personality_1.csv")
marriage<- read_csv("Variblenamefiles/marriage.csv")
ner_at<- read_csv("Variblenamefiles/nervous_attack.csv")
discrim<- read_csv("Variblenamefiles/discrimination.csv")
demograph<- read_csv("Variblenamefiles/demographics.csv")
family<- read_csv("Variblenamefiles/family.csv")
family_n_friends<- read_csv("Variblenamefiles/family_n_friends.csv")
depress<- read_csv("Variblenamefiles/depression.csv")
suicide<- read_csv("Variblenamefiles/Suicide.csv")


"Uncomment when uploading raw data however the raw dataset is too large for Git"
```

```{r}
#Read in Var names

#Main
eatdisord_1<- select(eatdisord_1, CPES, Eating_Disorder)
eatdisord_1= drop_na(eatdisord_1)
View(eatdisord_1)

#CPES
CPES_ed= select(eatdisord_1, CPES)
View(CPES_ed)

#Full_explaination
full_name= select(eatdisord_1, Eating_Disorder)
View(full_name)

#Make it a list
namelist = as.list(full_name)
'print(namelist)'
' We did not need this and can join on just the CPES code and maintain the information of the varible'
```

##Making Subset(eating disorder)

```{r}
data_ed= select(raw_data, CPES_ed$CPES[1:64])
View(data_ed)
```

#Substance varibles 
```{r}
#Main
sub_use_1<- select(sub_use_1, CPES)
sub_use_1= drop_na(sub_use_1)
#View(sub_use_1)

#Make it a list
namelist_su = as.list(sub_use_1)
data_su= select(raw_data, sub_use_1$CPES[1:70])
```

#Tobacco
```{r}
#Main
tobacco_1<- select(tobacco_1, CPES)
tobacco_1= drop_na(tobacco_1)
#Make it a list
namelist_to = as.list(tobacco_1)
data_to= select(raw_data, tobacco_1$CPES[1:65])
```

#Social Phobia
```{r}
#Main
social_ph<- select(social_ph, CPES)
social_ph= drop_na(social_ph)
#Make it a list
namelist_sph = as.list(social_ph)
data_sph= select(raw_data, social_ph$CPES[1:87])
```

#Personality
```{r}
#Main
persona<- select(persona, CPES)
persona= drop_na(persona)
#Make it a list
namelist_per = as.list(persona)
data_per= select(raw_data, namelist_per$CPES[1:44])
```

#Marriage
```{r}
#Main
marriage<- select(marriage, CPES)
marriage= drop_na(marriage)
#Make it a list
namelist_mar = as.list(marriage)
data_mar= select(raw_data, namelist_mar$CPES[1:29])
```

#Social Networks

```{r}
#Main
socnet<- select(socnet, CPES)
socnet= drop_na(socnet)
#Make it a list
namelist_sn = as.list(socnet)
data_sn= select(raw_data, namelist_sn$CPES[1:15])
```

#Nervous Attack
```{r}
#Main
ner_at<- select(ner_at, CPES)
ner_at= drop_na(ner_at)
#Make it a list
namelist_nerv = as.list(ner_at)
data_nerv= select(raw_data, namelist_nerv$CPES[1:23])
```

#Discrimination

```{r}
#Main
discrim<- select(discrim, CPES)
discrim= drop_na(discrim)
#Make it a list
namelist_disc = as.list(discrim)
data_disc= select(raw_data, namelist_disc$CPES[1:13])
```

#Demographics
```{r}
#Main
demograph<- select(demograph, CPES)
demograph= drop_na(demograph)
#Make it a list
namelist_dem= as.list(demograph)
data_dem= select(raw_data, namelist_dem$CPES[1:14])
```

#Family Cohesion

```{r}
#Main
family<- select(family, CPES)
family= drop_na(family)
#Make it a list
namelist_fam = as.list(family)
data_fam= select(raw_data, namelist_fam$CPES[1:15])
data_fam
```
#Family and Friends
```{r}
#Main
family_n_friends<- select(family_n_friends, CPES)
family_n_friends= drop_na(family_n_friends)
#Make it a list
namelist_ff = as.list(family_n_friends)
data_ff= select(raw_data, namelist_ff$CPES[1:39])
data_ff
```
#Depression Espoide
```{r}
#Main
depress<- select(depress, CPES)
depress= drop_na(depress)
#Make it a list
namelist_dep = as.list(depress)
data_dep= select(raw_data, namelist_dep$CPES[1:5])
data_dep
```

#Alcohol
```{r}
#Main
alcohol<- select(alcohol, CPES)
alcohol= drop_na(alcohol)
#Make it a list
namelist_alco = as.list(alcohol)
data_alco= select(raw_data, namelist_alco$CPES[1:5])
data_alco
```


#Suicide
```{r}
#Main
suicide<- select(suicide, CPES)
suicide= drop_na(suicide)
#Make it a list
namelist_sui = as.list(suicide)
data_sui= select(raw_data, namelist_sui$CPES[1:12])
data_sui
```

#Tree Models
```{r}
#tree model using alcohol as a predictor
alco = cbind(data_dep, data_alco)
alco
alco = alco%>%
  mutate(Depressed = as.factor(ifelse(V07876 == 1, 1, 0)))
set.seed(1)
train = alco %>%
  sample_n(10000)
test = alco %>%
  setdiff(train)
tree_alco = tree(Depressed ~ . - V07876, train, na.action = na.tree.replace)
tree_alco=tree(Depressed~., train)
tree_alco
summary(tree_alco)
tree_alco
plot(tree_alco)
text(tree_alco)
train

#logistic regression
glm_fit = glm(Depressed~. - V07876,
data = train,
family = binomial)
summary(glm_fit)
coefficients(glm_fit)

#a combination of depression, alcohol use, suicidality, and nervousness
#V01993: Seriously thought about committing suicide
#V02044: Ever attempted suicide
#V08312: ICD Alcohol Dependence (30 day)
combo1 <- cbind(data_dep, data_alco, data_sui, data_nerv)
combo1 <- combo1%>%
    mutate(Depressed = as.factor(ifelse(V07876 == 1, 1, 0)))


#LOGISTIC REGRESSION
glm_fit = glm(Depressed~ V01993 + V02044 + V08312,
  data = combo1,
  family = binomial)
summary(glm_fit)
coefficients(glm_fit)
```

<<<<<<< HEAD
=======
#DATA IMAGES
```{r}
sample1= data_alco%>%
  sample_n(1000)
a <- ggplot(sample1, aes(V08312))+geom_histogram()
a
```

```{r}
b <- ggplot(sample1, aes(V08515))+geom_histogram()
b
```

```{r}
sample2= data_su%>%
  sample_n(1000)
c <- ggplot(sample2, aes(V03336))+geom_histogram()
c
```

```{r}
d <- ggplot(sample2, aes(V03290)) +geom_histogram()
d
```

```{r}
sample3 = data_sph %>%
  sample_n(1000)
e <- ggplot(sample3, aes(V01533))+geom_histogram()  #social fear situation - fear vomiting
e
```

```{r}
f <- ggplot(sample3, aes(V01511)) + geom_histogram() #Shy/afraid/uncomf entering room when others are present
f
```

By looking at several sample variables in our data through histogram visualization, we have learned that in our data we have numerical variables, but there are bunch of categorical variables, (Yes or No). In our visualization of categorical variable, 1 indicates "Yes" and 5 indicates "No"" in x-axis, and we have different ranges of scales for y-axis. In our numerical variables, we have different scales in x and y-axis.

>>>>>>> 9f42ce87ef64fa276feec6dc649c9561a2bbaefc
