---
title: "Results-Checkin"
author: "BeeVee trade"
date: "November 26, 2018"
output: pdf_document
---


```{r, results='hide'}
library(haven)
library(tidyr)
library(dplyr)
library(mosaic)
library(tree)
library(ISLR)
library(ggplot2)
library(class)

```

#Impoting CSVs
```{r, results='hide'}
library(readr)
library(haven)
#raw_data <- read_sav("C:/Users/rocio/Downloads/20240-0001-Data.sav")
eatdisord_1 <- read_csv("Variblenamefiles/eatdisord_1.csv")
sub_use_1 <- read_csv("Variblenamefiles/sub_use_1.csv")
socnet<- read_csv("Variblenamefiles/socialnetworks.csv")
tobacco_1<- read_csv("Variblenamefiles/Tobacco_1.csv")
alcohol<- read_csv("Variblenamefiles/alcohol.csv")
social_ph<- read_csv("Variblenamefiles/Soicalph_1.csv")
persona<- read_csv("Variblenamefiles/personality_1.csv")
marriage<- read_csv("Variblenamefiles/marriage.csv")
ner_at<- read_csv("Variblenamefiles/nervous_attack.csv")
discrim<- read_csv("Variblenamefiles/discrimination.csv")
demograph<- read_csv("Variblenamefiles/demographics.csv")
family<- read_csv("Variblenamefiles/family.csv")
family_n_friends<- read_csv("Variblenamefiles/family_n_friends.csv")
depress<- read_csv("Variblenamefiles/depression.csv")
suicide<- read_csv("Variblenamefiles/Suicide.csv")


"Uncomment when uploading raw data however the raw dataset is too large for Git"

num_to_bin <- function(column) {
  
  column <-as.factor(column)
  
  column
}


```

```{r, results='hide'}
#Read in Var names

#Main
eatdisord_1<- select(eatdisord_1, CPES, Eating_Disorder)
eatdisord_1= drop_na(eatdisord_1)
View(eatdisord_1)

#CPES
CPES_ed= select(eatdisord_1, CPES)
View(CPES_ed)

#Full_explaination
full_name= select(eatdisord_1, Eating_Disorder)
View(full_name)

#Make it a list
namelist = as.list(full_name)
'print(namelist)'
' We did not need this and can join on just the CPES code and maintain the information of the varible'
```

#Eating Disorder

```{r, results='hide'}
data_ed= select(raw_data, CPES_ed$CPES[1:64])
View(data_ed)
```

#Eating disorder

```{r, results='hide'}
data_ed= select(raw_data, CPES_ed$CPES[1:64])
data_ed2= select(raw_data, CPES_ed$CPES[1:64])
```
#Substance varibles 
```{r, results='hide'}
#Main
sub_use_1<- select(sub_use_1, CPES)
sub_use_1= drop_na(sub_use_1)
#View(sub_use_1)

#Make it a list
namelist_su = as.list(sub_use_1)
data_su= select(raw_data, sub_use_1$CPES[1:70])
```

#Tobacco
```{r, results='hide'}
#Main
tobacco_1<- select(tobacco_1, CPES)
tobacco_1= drop_na(tobacco_1)
#Make it a list
namelist_to = as.list(tobacco_1)
data_to= select(raw_data, tobacco_1$CPES[1:65])
```

#Social Phobia
```{r, results='hide'}
#Main
social_ph<- select(social_ph, CPES)
social_ph= drop_na(social_ph)
#Make it a list
namelist_sph = as.list(social_ph)
data_sph= select(raw_data, social_ph$CPES[1:87])
```

#Personality
```{r, results='hide'}
#Main
persona<- select(persona, CPES)
persona= drop_na(persona)
#Make it a list
namelist_per = as.list(persona)
data_per= select(raw_data, namelist_per$CPES[1:44])
```

#Marriage
```{r, results='hide'}
#Main
marriage<- select(marriage, CPES)
marriage= drop_na(marriage)
#Make it a list
namelist_mar = as.list(marriage)
data_mar= select(raw_data, namelist_mar$CPES[1:29])

data_mar <- apply(data_mar, 2, FUN = num_to_bin)
summary(data_mar)
```

#Social Networks

```{r, results='hide'}
#Main
socnet<- select(socnet, CPES)
socnet= drop_na(socnet)
#Make it a list
namelist_sn = as.list(socnet)
data_sn= select(raw_data, namelist_sn$CPES[1:15])
data_sn <- apply(data_sn, 2, FUN = num_to_bin)
summary(data_sn)
```

#Nervous Attack
```{r, results='hide'}
#Main
ner_at<- select(ner_at, CPES)
ner_at= drop_na(ner_at)
#Make it a list
namelist_nerv = as.list(ner_at)
data_nerv= select(raw_data, namelist_nerv$CPES[1:23])
data_nerv <- apply(data_nerv, 2, FUN = num_to_bin)
summary(data_nerv)

```

#Discrimination

```{r, results='hide'}
#Main
discrim<- select(discrim, CPES)
discrim= drop_na(discrim)
#Make it a list
namelist_disc = as.list(discrim)
data_disc= select(raw_data, namelist_disc$CPES[1:13])
data_disc <- apply(data_disc, 2, FUN = num_to_bin)
summary(data_disc)

```

#Demographics
```{r, results='hide'}
#Main
demograph<- select(demograph, CPES)
demograph= drop_na(demograph)
#Make it a list
namelist_dem= as.list(demograph)
data_dem= select(raw_data, namelist_dem$CPES[1:14])
data_dem <- apply(data_dem, 2, FUN = num_to_bin)
summary(data_dem)
```

#Family Cohesion

```{r, results='hide'}
#Main
family<- select(family, CPES)
family= drop_na(family)
#Make it a list
namelist_fam = as.list(family)
data_fam= select(raw_data, namelist_fam$CPES[1:15])
data_fam <- apply(data_fam, 2, FUN = num_to_bin)
summary(data_fam)
```
#Family and Friends
```{r, results='hide'}
#Main
family_n_friends<- select(family_n_friends, CPES)
family_n_friends= drop_na(family_n_friends)
#Make it a list
namelist_ff = as.list(family_n_friends)
data_ff= select(raw_data, namelist_ff$CPES[1:39])

data_ff <- apply(data_ff, 2, FUN = num_to_bin)
summary(data_ff)
```
#Depression Espoide
```{r, results='hide'}
#Main
depress<- select(depress, CPES)
depress= drop_na(depress)
#Make it a list
namelist_dep = as.list(depress)
data_dep= select(raw_data, namelist_dep$CPES[1:5])
data_dep <- apply(data_dep, 2, FUN = num_to_bin)
summary(data_dep)
```

#Alcohol
```{r, results='hide'}
#Main
alcohol<- select(alcohol, CPES)
alcohol= drop_na(alcohol)
#Make it a list
namelist_alco = as.list(alcohol)
data_alco= select(raw_data, namelist_alco$CPES[1:5])
data_alco <- apply(data_alco, 2, FUN = num_to_bin)
summary(data_alco)
```


#Suicide
```{r, results='hide'}
#Main
suicide<- select(suicide, CPES)
suicide= drop_na(suicide)
#Make it a list
namelist_sui = as.list(suicide)
data_sui= select(raw_data, namelist_sui$CPES[1:12])

data_sui <- apply(data_sui, 2, FUN = num_to_bin)
summary(data_sui)

```
#Fixing the Varibles
the binary varibles are in the code as numeric and so we must change these to categorical
##Eating disorder
```{r}
data_ed = apply(data_sui, 2, FUN = num_to_bin)
# #Created Binary categorical for yes and No 
# data_ed$V04657<- as.factor(data_ed$V04657)
# data_ed$V04658<- as.factor(data_ed$V04658)
# data_ed$V04665<- as.factor(data_ed$V04665)
# data_ed$V04666<- as.factor(data_ed$V04666)
# data_ed$V04668<- as.factor(data_ed$V04668)
# data_ed$V04669<- as.factor(data_ed$V04669)
# data_ed$V04671<- as.factor(data_ed$V04671)
# data_ed$V04683<- as.factor(data_ed$V04683)
# data_ed$V04684<- as.factor(data_ed$V04684)
# data_ed$V04685<- as.factor(data_ed$V04685)
# data_ed$V04686<- as.factor(data_ed$V04686)
# data_ed$V04687<- as.factor(data_ed$V04687)
# data_ed$V04688<- as.factor(data_ed$V04688)
# data_ed$V04689<- as.factor(data_ed$V04689)
# data_ed$V04690<- as.factor(data_ed$V04690)
# data_ed$V04691<- as.factor(data_ed$V04691)
# data_ed$V04692<- as.factor(data_ed$V04692)
# data_ed$V04703<- as.factor(data_ed$V04703)
# data_ed$V04704<- as.factor(data_ed$V04704)
# data_ed$V04705<- as.factor(data_ed$V04705)
# data_ed$V04706<- as.factor(data_ed$V04706)
# data_ed$V04707<- as.factor(data_ed$V04707)
# data_ed$V04708<- as.factor(data_ed$V04708)
# data_ed$V04709<- as.factor(data_ed$V04709)
# data_ed$V04711<- as.factor(data_ed$V04711)
# data_ed$V04716<- as.factor(data_ed$V04716)
# data_ed$V04733<- as.factor(data_ed$V04733)
# data_ed$V04734<- as.factor(data_ed$V04734)
# data_ed$V04736<- as.factor(data_ed$V04736)
# data_ed$V04737<- as.factor(data_ed$V04737)
# data_ed$V04740<- as.factor(data_ed$V04740)
# data_ed$V04741<- as.factor(data_ed$V04741)
# data_ed$V04745<- as.factor(data_ed$V04745)
# data_ed$V04746<- as.factor(data_ed$V04746)
# data_ed$V04747<- as.factor(data_ed$V04747)
# data_ed$V04748<- as.factor(data_ed$V04748)
# data_ed$V04749<- as.factor(data_ed$V04749)
# data_ed$V04750<- as.factor(data_ed$V04750)
# data_ed$V04751<- as.factor(data_ed$V04751)
# data_ed$V04752<- as.factor(data_ed$V04752)
# data_ed$V04753<- as.factor(data_ed$V04753)
# data_ed$V04759<- as.factor(data_ed$V04759)
# data_ed$V04762<- as.factor(data_ed$V04762)
# data_ed$V04763<- as.factor(data_ed$V04763)
# 
# summary(data_ed[1:64])
```

##Substance Use

```{r}
data_su <- apply(data_su, 2, FUN = num_to_bin)
```

##Tobacco

```{r}

data_to<- apply(data_to, 2, FUN = num_to_bin)
```


## Social Phobia factor conversion [1:87]
```{r, results='hide'}
data_sph<- apply(data_sph, 2, FUN = num_to_bin)
# data_sph$V01504<- as.factor(data_sph$V01504)
# data_sph$V01505<- as.factor(data_sph$V01505)
# data_sph$V01506<- as.factor(data_sph$V01506)
# data_sph$V01507<- as.factor(data_sph$V01507)
# data_sph$V01508<- as.factor(data_sph$V01508)
# data_sph$V01509<- as.factor(data_sph$V01509)
# data_sph$V01510<- as.factor(data_sph$V01510)
# data_sph$V01511<- as.factor(data_sph$V01511)
# data_sph$V01512<- as.factor(data_sph$V01512)
# data_sph$V01513<- as.factor(data_sph$V01513)
# data_sph$V01514<- as.factor(data_sph$V01514)
# data_sph$V01515<- as.factor(data_sph$V01515)
# data_sph$V01516<- as.factor(data_sph$V01516)
# data_sph$V01517<- as.factor(data_sph$V01517)
# data_sph$V01529<- as.factor(data_sph$V01529)
# data_sph$V01530<- as.factor(data_sph$V01530)
# data_sph$V01531<- as.factor(data_sph$V01531)
# data_sph$V01532<- as.factor(data_sph$V01532)
# data_sph$V01533<- as.factor(data_sph$V01533)
# data_sph$V01534<- as.factor(data_sph$V01534)
# data_sph$V01535<- as.factor(data_sph$V01535)
# data_sph$V01536<- as.factor(data_sph$V01536)
# data_sph$V01537<- as.factor(data_sph$V01537)
# data_sph$V01538<- as.factor(data_sph$V01538)
# data_sph$V01539<- as.factor(data_sph$V01539)
# data_sph$V01540<- as.factor(data_sph$V01540)
# data_sph$V01541<- as.factor(data_sph$V01541)
# data_sph$V01542<- as.factor(data_sph$V01542)
# data_sph$V01543<- as.factor(data_sph$V01543)
# data_sph$V01544<- as.factor(data_sph$V01544)
# data_sph$V01545<- as.factor(data_sph$V01545)
# data_sph$V01546<- as.factor(data_sph$V01546)
# data_sph$V01547<- as.factor(data_sph$V01547)
# data_sph$V01548<- as.factor(data_sph$V01548)
# data_sph$V01549<- as.factor(data_sph$V01549)
# data_sph$V01551<- as.factor(data_sph$V01551)
# data_sph$V01552<- as.factor(data_sph$V01552)
# data_sph$V01553<- as.factor(data_sph$V01553)
# data_sph$V01554<- as.factor(data_sph$V01554)
# data_sph$V01555 <- as.factor(data_sph$V01555)
# data_sph$V01556 <- as.factor(data_sph$V01556)
# data_sph$V01557 <- as.factor(data_sph$V01557)
# data_sph$V01558 <- as.factor(data_sph$V01558)
# data_sph$V01561 <- as.factor(data_sph$V01561)
# data_sph$V01571 <- as.factor(data_sph$V01571)
# data_sph$V01583 <- as.factor(data_sph$V01583)
# data_sph$V01584 <- as.factor(data_sph$V01584)
# data_sph$V01597 <- as.factor(data_sph$V01597)
# data_sph$V01598 <- as.factor(data_sph$V01598)
# data_sph$V01601 <- as.factor(data_sph$V01601)
# data_sph$V01602 <- as.factor(data_sph$V01602)
# data_sph$V01603 <- as.factor(data_sph$V01603)
# data_sph$V01604 <- as.factor(data_sph$V01604)
# data_sph$V01605 <- as.factor(data_sph$V01605)
# data_sph$V01606 <- as.factor(data_sph$V01606)
# data_sph$V01607 <- as.factor(data_sph$V01607)
# data_sph$V01608 <- as.factor(data_sph$V01608)
# data_sph$V01609 <- as.factor(data_sph$V01609)
# data_sph$V01614 <- as.factor(data_sph$V01614)
# data_sph$V01615 <- as.factor(data_sph$V01615)
# data_sph$V01616 <- as.factor(data_sph$V01616)
# data_sph$V01617 <- as.factor(data_sph$V01617)
# data_sph$V01621 <- as.factor(data_sph$V01615)
# data_sph$V01615 <- as.factor(data_sph$V01615)
# data_sph$V01616 <- as.factor(data_sph$V01616)
# data_sph$V01617 <- as.factor(data_sph$V01617)
# data_sph$V01621 <- as.factor(data_sph$V01621)
# data_sph$V01622 <- as.factor(data_sph$V01622)
```

## Alcohol
```{r, results='hide'}
# data_alco$V08312 <-as.factor(ifelse(data_alco$V08312== 1,1,0))
# data_alco$V08311 <-as.factor(ifelse(data_alco$V08311== 1,1,0))
# data_alco$V08515 <-as.factor(ifelse(data_alco$V08515== 1,1,0))
```

```{r}
#a combination of depression, alcohol use, suicidality, and nervousness
#V01993: Seriously thought about committing suicide
#V02044: Ever attempted suicide
#V08312: ICD Alcohol Dependence (30 day)
combo1 <- cbind(data_dep, data_alco, data_sui, data_nerv)
combo1 <- na.omit(combo1)


#V03234: Often feel empty inside
#V01993: Seriously thought about committing suicide
#V02044: Ever attempted suicide
#V08312: ICD Alcohol Dependence (30 day)
#V03256: Feel uncomfortabe/helpless when alone

combo2 <- cbind(data_alco, data_per, data_sui, data_dep)%>%
  mutate(Depressed = V07876)%>%
  select(V07876, V03234,V01993, V02044, V08312, V03256) 
combo2 =  na.omit(combo2)


#LOGISTIC REGRESSION
glm_fit = glm(V07876~ .,
  data = combo2,
  family = binomial)
summary(glm_fit)
coefficients(glm_fit)

```

